### 2023-02-02 manuscript.tex
citations [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/436f3638b53adb35135c7589db39c8bbbb3d3df9.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/436f3638b53adb35135c7589db39c8bbbb3d3df9/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4073763121

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/8f0433b6c923287d3a404c9434df00f9e47b172a/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/8f0433b6c923287d3a404c9434df00f9e47b172a}{stain/2022-fdo-paper@8f0433b}
on February 2, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/436f3638b53adb35135c7589db39c8bbbb3d3df9/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/436f3638b53adb35135c7589db39c8bbbb3d3df9}{stain/2022-fdo-paper@436f363}
on February 2, 2023.
